---
title: 函数式编程语言中常见的高阶函数(in R)
author: RStudio
date: '2018-12-17'
slug: 函数式编程语言中常见的高阶函数-in-r
categories:
  - R
tags:
  - programming
css: []
description: ''
highlight: yes
index: no
scripts: []
---



**在列表对象上循环**   
`lapply`:**输入**`list`对象，**返回**与x等长的`list`对象   
`sapply`:是`lapply`的用户友好版本，默认情况下，返回向量或矩阵。   
`endoapply` 与`mendoapply`类似于`lapply`和`sapply`，不过返回的对象与输入对象的类型一致，而不是`list`   

`revElements(x,i)`:倒序输入`list`对象x，`i`指定list index   


`pc`:返回与输入对象具有相同长度的列表或List对象。   

**List对象的函数编程方法**   

**FROM**: `?base::Reduce`   

```{r echo=TRUE,include=T,eval=FALSE}
# Usage   
Reduce(f,x,init,right = FALSE,accumulate = FALSE)
Filter(f,x)
Find(f,x,right = FALSE, nomatch = NULL)
Map(f)
Negate(f)
Position(f, x, right = FALSE, nomatch = NA_integer_)
```   
**Arguments**   

|args|description|
|----|----------------------------------------------------------------------|
f|a function of the appropriate arity (binary for Reduce, unary for Filter, Find and Position, k-ary for Map if this is called with k arguments). An arbitrary predicate function for Negate.
x|a vector.
init|an R object of the same kind as the elements of x.
right|a logical indicating whether to proceed from left to right (default) or from right to left.
accumulate|a logical indicating whether the successive reduce combinations should be accumulated. By default, only the final combination is used.
nomatch|the value to be returned in the case when “no match” (no element satisfying the predicate) is found.
...|vectors.



**List对象中表达式的计算**   
```{r echo=TRUE,include=TRUE,eval=FALSE}
# Usage
with(data, expr, ...)
within(data, expr, ...)

```



**将列表合并到矩阵中**   
```{r echo=TRUE,include=TRUE,eval=FALSE}
rbind(..., deparse.level=1L)
cbind(..., deparse.level=1L)
```
